Robust DPG stability II

### 2012-04-04 docs/NewBCRobustness_paper/paper.tex
correct my last name
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@435 36274a68-8941-4c93-80ef-affaed5139da
some fast corrections and comments need to be resolved
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@436 36274a68-8941-4c93-80ef-affaed5139da

\author{Tan Bui \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
\title{Robust DPG stability II}
\date{}
\begin{document}

@@

The DPG (discontinuous Petrov-Galerkin) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation". For a given operator equation in strong form $Au = f$, the ultra-weak formulation is
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
\]
where $A^*$ is the formal adjoint resulting from integration by parts, and $[v]$ is the jump of the test function $v$ across element boundaries.  Both the inner product and formal adjoint are understood in an element-wise fashion. Under the ultra-weak formulation, the regularity requirement on each solution variable is relaxed through integration by parts.  Moreover, to maintain conformity while seeking an $L^2$ setting on interior ``field" variables, boundary terms are identified as additional new unknowns.  The result is a hybridized DG method with locally supported optimal test functions, with energy setting 
\begin{align*}
u&\in L^2(\Omega)\\
v&\in V=D(A^*) \\
\widehat{u}&\in T(D(A))
\end{align*}
where $D(A^*)$ is the domain of the formal adjoint $A^*$, and $T(D(A))$ is the trace space of the domain of the operator $A$ in its strong form. A more comprehensive discussion of the abstract setting of DPG, as well as a proof of well-posedness, is developed using the graph norm in \cite{DPGFriedrichs}.

@@

Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.  The energy norm in which DPG is optimal 
\[
\|u\|_E = \sup \frac{b(u,v)}{\|v\|_V}.
\]
depends heavily on our choice of norm on the test space $\|v\|_V$.

@@

Our aim now is to translate the above abstract language to a concrete model problem in computational fluid dynamics.  We consider the model convection-diffusion problem on domain $\Omega \in \mathbb{R}^d$ with boundary $\Gamma$
\begin{align}
\div (\beta u) - \epsilon\Delta v &= f  \label{primal}
\end{align}
in first order form
\begin{align*}
\div (\beta u - \sigma) &= f  \\
\frac{1}{\epsilon}\sigma - \grad u &= 0
\end{align*}
with the corresponding variational form (prior to the application of boundary conditions)
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle 
\end{align*}
where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$ across an element edge, defined as
\begin{align*}
\left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
\left[ v\right] &= v^+{\rm sgn}(n^+) + v^-{\rm sgn}(n^-)
\end{align*}
where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given global orientation, and $-1$ otherwise. \textcolor{red}{I need to find more simple way to explain sgn}.

@@

 The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are element-wise ``broken" Sobolev spaces.  By duality, $\widehat{u}$ lives in $H^{1/2}(\Gamma_h)$, the trace space of $H^1(\Omega_h)$, while $\widehat{f}_n$ comes from $H^{-1/2}(\Gamma_h)$, the normal trace space of $H({\rm div},\Omega_h)$.

Finally, we split the boundary $\Gamma$ into three portions
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm (inflow)}\\
\Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\} \quad {\rm (outflow)}\\
\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\}
\end{align*}
We adopt a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n = f_n = u_0
\]
on $\Gamma_-$, and continue with the wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem, as for many problems of interest in computational fluid dynamics, we expect $\grad u$ to be small near the inflow, and that the solutions to \eqref{primal} using $u=u_0$ and $\beta_n u - \sigma_n = f_n = u_0$ should converge to each other for sufficiently small $\epsilon$.  Under these new boundary conditions, our variational problem $b(u,v) = l(v)$ is now defined by
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} + \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup \Gamma_h^0} \\
l\left(\left(\tau,v\right)\right) &= \left(f, v\right) + \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_+} - \langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_-} 
\end{align*}

@@

Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we can now also define the trace norms as (canonical) minimum energy extension norms (taking into account the respective lifts/boundary conditions on $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and $\Gamma_-$, respectively)
\begin{align*}
\|\widehat{u}\| &= \inf_{w\in H^1(\Omega), \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\
\|\widehat{f}_n\| &= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}= 0, \left. q\cdot n \right |_{\Gamma_h} = \widehat{f}_n} \|q\|_{H({\rm div},\Omega)}
\end{align*}
%Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
%\begin{align*}
%\|u\| &= \|u\|_{L^2} \\
%\|\sigma\| &= \|\sigma\|_{L^2(\Omega_h)}
%\end{align*}
We will construct norms on $U$ as combinations of norms on each variable
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1 \|u\|_{L^2(\Omega_h)} + C_2 \|\sigma\|_{L^2(\Omega_h)} + C_3 \|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]
\subsection{Norms on $V$}

%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will construct norms on $v$ and $\tau$ using some combination of terms which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$ norm over a single element
\[
\|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)} = \|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2  + \|\tau\|_{L^2(K)}^2 + \|\div \tau\|_{L^2(K)}^2
\]
The squared norm over the entire triangulation $\Omega_h$ is defined to be the squared sum of contributions from each element
\[
\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)} = \sum_{K\in \Omega_h} \|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)}
\]
The exact norms that we will specify on $V$ will be determined later.

@@

\subsection{Approximability of the quasi-optimal test norm}%\textcolor{red}{Make new subsection on robustness here, reorganize}}

For convection-diffusion, the quasi-optimal test norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v \|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 + C_1\|v\|_{L^2} + C_2\|\tau\|_{L^2}
\]
for some choice of constants $C_1$ and $C_2$.  
%We note that the optimal test norm will automatically guarantee the robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.  
However, use of this norm for the convection-diffusion problem is difficult - the variational problem for optimal test functions using the quasi-optimal test norm is equivalent to a reaction-diffusion system \cite{DBLP:journals/procedia/NiemiCC11}.  Such systems also develop strong boundary layers for small diffusion, and transforming the problem to the reference element reveals that the inversion of the inner product associated with the optimal test norm will induce strong boundary layers of width $\epsilon/h^2$ in the optimal test functions.  In comparison, the quasi-optimal norm has yielded fantastic results for the Helmholtz equation and other wave propagation problems. The difference between the two problems lies in the fact that, for wave propagation problems, the mesh size tends to be on the order of the wavenumber $k$/singular perturbation parameter. Transforming the variational problem using the quasi-optimal test norm for wave propagation yields smooth optimal test functions that are much easier to approximate over the reference element. Typically, the wavenumbers $k$ of physical interest are $O(100)-O(1000)$ with respect to a unit domain. The corresponding finite element problems will typically be solved on meshes containing approximately $O(k^d)$ elements in $\mathbb{R}^d$, well within the range of a computationally tractable simulation. However, for convection diffusion problems, the relevant range of $\epsilon$ for physical problems can be as small as $1e-7$. Solving on partially under-resolved meshes is thus unavoidable, and the approximability of the optimal test functions must be addressed in order to take advantage of the properties of DPG.

@@

The estimates and proofs in this paper are largely based off of techniques and prior work done in \cite{DPGrobustness} and \cite{analysisDPG}; for further details, we encourage readers to consult these two publications as well\footnote{The primary contributions in this paper are stronger stability estimates for a new inflow boundary condition and a slightly different test norm.}.

@@

The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.  
%The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
%\[
%\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
%\]
%where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.  Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments. We focus first on quantifying the condition on robustness. Such a condition is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$ 
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
\]
where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$. %The robust bound on the error in $\|\cdot\|_E$ from below by error in $\|\cdot\|_{U,1}$ is crucial to avoiding the instabilities associated with loss of robustness - 
\textcolor{red}{Explain in intuitive terms what the bounds above and below mean.}
Our goal is to explicitly derive the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ that characterize this relation, taking into account the limiting case of $\epsilon \rightarrow 0$.

>>>>

\author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
\title{Robust DPG stability II}
\date{}
\begin{document}

@@

The discontinuous Petrov-Galerkin (DPG) method is the pairing of the concept of locally computable optimal test functions with the so-called ``ultra-weak formulation". For a given operator equation in strong form $Au = f$, the ultra-weak formulation is
\[
b\left(\left(\widehat{u},u\right),v\right) - l(v) = \langle \widehat{u}, [v] \rangle - (u,A^*v) - (f,v) = 0
\]
where $A^*$ is the formal adjoint resulting from integration by parts,
and $[v]$ is the jump of the test function $v$ across element
boundaries.  Both the inner product and formal adjoint are understood
in an element-wise fashion. Under the ultra-weak formulation, the
regularity requirement on each solution variable is relaxed through
integration by parts.  Moreover, to maintain conformity while seeking
an $L^2$ setting on interior ``field" variables, boundary terms are
identified as additional new unknowns.  The result is a hybridized DG \textcolor{blue}{TB: This is not true, the hybridized DG method does not hybridize both traces/fluxes}
method with locally supported optimal test functions, with energy
setting
\begin{align*}
u&\in L^2(\Omega)\\
v&\in V=D(A^*) \\
\widehat{u}&\in T(D(A))
\end{align*}
where $D(A^*)$ is the domain of the formal adjoint $A^*$, and $T(D(A))$ is the trace space of the domain of the operator $A$ in its strong form. A more comprehensive discussion of the abstract setting of DPG, as well as a proof of well-posedness, is developed using the graph norm in \cite{DPGFriedrichs}.

@@

Up to now, we have neglected discussion of the proper choice of inner product/norm on the space $V$.  The energy norm in which DPG is optimal 
\[
\|u\|_E = \sup_{v \in V\setminus \{0\}} \frac{b(u,v)}{\|v\|_{V,E}}.
\]
depends heavily on our choice of norm on the test space $\|v\|_{V,E}$.

@@

Our aim now is to translate the above abstract language to a concrete model problem in computational fluid dynamics.  We consider the model convection-diffusion problem on domain $\Omega \in \mathbb{R}^d$ with boundary $\Gamma$
\begin{align}
\div (\beta u) - \epsilon\Delta v &= f  \label{primal}
\end{align}
in first order form
\begin{align*}
\div (\beta u - \sigma) &= f  \\
\frac{1}{\epsilon}\sigma - \grad u &= 0
\end{align*}
with the corresponding variational form (prior to the application of boundary conditions)
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right), \left(\tau, v\right)\right) = \left(u,\div \tau - \beta \cdot \grad v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle \left[\tau_n\right], \widehat{u} \rangle + \langle \widehat{f}_n, \left[v\right] \rangle 
\end{align*}
where $\left[ \tau_n \right]$ and $\left[ v\right]$ denote the jumps in $\tau_n$ and $v$ across an element edge, defined as
\begin{align*}
\left[ \tau_n \right] &= \tau^+ \cdot n^+ + \tau^-\cdot n^-\\
\left[ v\right] &= v^+{\rm sgn}(n^+) + v^-{\rm sgn}(n^-)
\end{align*}
where $n$ is the outward normal vector to an element edge, and ${\rm sgn}(n)$ is 1 if $n$ aligns with a given global orientation, and $-1$ otherwise. \textcolor{red}{I need to find more simple way to explain sgn} \textcolor{blue}{TB: see my DPG Friedrichs paper for the explanation}.

@@

 The functional setting is now well understood as well (see \cite{analysisDPG} for details) - $u,\sigma \in L^2(\Omega)$, $v \in H^1(\Omega_h)$, $\tau \in H({\rm div},\Omega_h)$, where $H^1(\Omega_h)$ and $H({\rm div},\Omega_h)$ are ``broken" Sobolev spaces.  By duality, $\widehat{u}$ lives in $H^{1/2}(\Gamma_h)$, the trace space of $H^1(\Omega_h)$, while $\widehat{f}_n$ comes from $H^{-1/2}(\Gamma_h)$, the normal trace space of $H({\rm div},\Omega_h)$.

Finally, we split the boundary $\Gamma$ into three portions
\begin{align*}
\Gamma_{-} &\coloneqq \{x\in \Gamma; \beta_n(x) < 0\} \quad {\rm (inflow)}\\
\Gamma_{+} &\coloneqq \{x\in \Gamma; \beta_n(x) > 0\} \quad {\rm (outflow)}\\
\Gamma_{0} &\coloneqq \{x\in \Gamma; \beta_n(x) = 0\}
\end{align*}
We adopt a new inflow boundary condition, given by Hesthaven et al in \cite{Hesthaven96astable}, where we set
\[
\beta_n u - \sigma_n = f_n = u_0
\]
on $\Gamma_-$, and continue \textcolar{blue}{TB: from where?} with the
wall boundary condition $u=0$ on $\Gamma_+$.  For our model problem,
as for many problems of interest in computational fluid dynamics, we
expect $\grad u$ to be small near the inflow, and that the solutions
to \eqref{primal} using $\beta_n u - \sigma_n = f_n = u_0$ on $\Gamma_-$
will converge to that using $u=u_0$ on $\Gamma_-$  for sufficiently small $\epsilon$.
Under these new boundary conditions, our variational problem $b(u,v) =
l(v)$ is now defined by
\begin{align*}
b\left(\left(u,\sigma, \widehat{u}, \widehat{\sigma}_n\right),
\left(\tau, v\right)\right) &= \left(u,\div \tau - \beta \cdot \grad
v\right) + \left(\sigma, \epsilon^{-1} \tau + \grad v\right) - \langle
\left[\tau_n\right], \widehat{u} \rangle_{\Gamma_-\cup \Gamma_h^0} +
\langle \widehat{f}_n, \left[v\right] \rangle_{\Gamma_+ \cup
  \Gamma_h^0} \\ l\left(\left(\tau,v\right)\right) &= \left(f,
v\right) %+ \langle \left[\tau_n\right], \widehat{u} \rangle_{\Gamma_+}
- \langle u_0, v \rangle_{\Gamma_-}
\end{align*}

@@

Given the boundary conditions on $\widehat{u}$ and $\widehat{f}_n$, we
can now also define the trace norms as (canonical) minimum energy
extension norms (taking into account the respective lifts/boundary
conditions on $\widehat{u}$ and $\widehat{f}_n$ on $\Gamma_+$ and
$\Gamma_-$, respectively)
\begin{align*}
\|\widehat{u}\| &= \inf_{w\in H^1(\Omega),
  \left.w\right|_{\Gamma_+}=0, \left.w\right |_{\Gamma_h\setminus
    \Gamma_+ } = \widehat{u}} \|w\|_{H^1(\Omega)}\\ \|\widehat{f}_n\|
&= \inf_{q\in H({\rm div},\Omega), \left.q\cdot n\right|_{\Gamma_-}=
  0, \left. q\cdot n \right |_{\Gamma_h\setminus
    \Gamma_-} = \widehat{f}_n}
\|q\|_{H({\rm div},\Omega)}
\end{align*}
%Additionally, throughout the rest of this work, we denote norms on $u$ and $\sigma$ as
%\begin{align*}
%\|u\| &= \|u\|_{L^2} \\
%\|\sigma\| &= \|\sigma\|_{L^2(\Omega_h)}
%\end{align*}
We will construct norms on $U$ as combinations of norms on each variable
\[
\left\|\left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right\|_U = C_1
\|u\|_{L^2(\Omega_h)} + C_2 \|\sigma\|_{L^2(\Omega_h)} + C_3
\|\widehat{u}\| + C_4 \|\widehat{f}_n\|.
\]
\subsection{Norms on $V$}

%We will denote $\|\cdot \| = \|\cdot\|_{L^2}$ for all functions defined on $\Omega_h$. 
As $\tau \in H({\rm div},\Omega_h)$ and $v \in H^1(\Omega_h)$, we will
construct norms on $v$ and $\tau$ using some combination of terms
which are equivalent to the canonical $H^1(K) \times H({\rm div},K)$
norm over a single element
\[
\|\left(\tau,v\right)\|_{H^1(K) \times H({\rm div},K)}^2 =
\|v\|_{L^2(K)}^2 + \|\grad v\|_{L^2(K)}^2 + \|\tau\|_{L^2(K)}^2 +
\|\div \tau\|_{L^2(K)}^2
\]
The squared norm over the entire triangulation $\Omega_h$ is defined to be the squared sum of contributions from each element
\[
\|\left(\tau,v\right)\|_{H^1(\Omega_h) \times H({\rm div},\Omega_h)}^2
= \sum_{K\in \Omega_h} \|\left(\tau,v\right)\|_{H^1(K) \times H({\rm
    div},K)}^2
\]
The exact norms that we will specify on $V$ will be determined later.

@@

\subsection{Approximability of the quasi-optimal test norm}
\textcolor{blue}{need to define what we mean by robustness. perharps the best place is in the introduction}

For convection-diffusion, the quasi-optimal test norm is 
\[
\|\left(\tau, v\right)\|_V^2 = \| \div \tau - \beta \cdot \grad v
\|_{L^2}^2 + \| \epsilon^{-1} \tau + \grad v \|_{L^2}^2 +
C_1\|v\|_{L^2}^2 + C_2\|\tau\|_{L^2}^2
\]
for some choice of constants $C_1$ and $C_2$.  
%We note that the optimal test norm will automatically guarantee the
%robust bound $\|\left(\tau, v\right)\|_V \leq \|u\|_{L^2}$.
However, use of this norm for the convection-diffusion problem is
difficult - the variational problem for optimal test functions using
the quasi-optimal test norm is equivalent to a reaction-diffusion
system \cite{DBLP:journals/procedia/NiemiCC11}.  Such systems also
develop strong boundary layers for small diffusion, and transforming
the problem to the reference element reveals that the inversion of the
inner product associated with the optimal test norm will induce strong
boundary layers of width $\epsilon/h^2$ in the optimal test functions.
In comparison, the quasi-optimal norm has yielded fantastic
\textcolor{blue}{we don't use fantastic in technical English, replace
  it with excellent, for example} results for the Helmholtz equation
and other wave propagation problems. The difference between the two
problems lies in the fact that, for wave propagation problems, the
mesh size tends to be on the order of the wavenumber $k$/singular
perturbation parameter. Transforming the variational problem using the
quasi-optimal test norm for wave propagation yields smooth optimal
test functions that are much easier to approximate over the reference
element. Typically, the wavenumbers $k$ of physical interest are
$O(100)-O(1000)$ with respect to a unit domain. The corresponding
finite element problems will typically be solved on meshes containing
approximately $O(k^d)$ elements in $\mathbb{R}^d$, well within the
range of a computationally tractable simulation. However, for
convection diffusion problems, the relevant range of $\epsilon$ for
physical problems can be as small as $1e-7$. Solving on partially
under-resolved meshes is thus unavoidable, and the approximability of
the optimal test functions must be addressed in order to take
advantage of the properties of DPG.

@@

The estimates and proofs in this paper are largely based on previous
work done in \cite{DPGrobustness} and \cite{analysisDPG}. Our primary
contributions in this paper are stronger stability estimates for a new
inflow boundary condition and a slightly different test norm.

@@

The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm \textit{that does not lose robustness as $\epsilon \rightarrow 0$}.  
%The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
%\[
%\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
%\]
%where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.  Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments. We focus first on quantifying the condition on robustness. Such a condition is equivalent to showing the robust boundedness of the energy error from above and below by norms on $U$ 
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
\]
\textcolor{blue}{As a reader, up to this point, I don't understand what robustness means and why the above double inequalities is the condition for robustness?}
where $\lesssim$ denotes a bound by a constant that will not grow as $\epsilon \rightarrow 0$. %The robust bound on the error in $\|\cdot\|_E$ from below by error in $\|\cdot\|_{U,1}$ is crucial to avoiding the instabilities associated with loss of robustness - 
\textcolor{red}{Explain in intuitive terms what the bounds above and below mean.}
Our goal is to explicitly derive the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ that characterize this relation, taking into account the limiting case of $\epsilon \rightarrow 0$.
